---
title: "DSIEUR Wrap-up"
subtitle: "Chapters 17-19"
author: "Ryan Woodbury"
date: "5/26/2021"
output: 
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
        highlightStyle: github
        conIncrementalSlides: false
        ratio: '16:9'
---

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#1c5253",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(cache = TRUE)
```


class: middle

# DSIEUR Wrap-up

- Chapter 17: Learning More
- Chapter 18: Additional Resources
- Chapter 19: Conclusion: Where to Next?
- Sharing with our communities

---

class: middle

# Chapter 17: Learning More
- Adopt a Growth Mindset (vs. a Fixed Mindset)
- Discover New Information
  - See Chapter 18
- Ask for Help
  - Where? Who?
- Share What You've Learned
  - Where? How?
- Welcome Others


---

class: middle

# Chapter 18: Additional Resources

There are a ton of books, articles, chapters, workshops, and videos referenced.  
What are your go-to recommendations for learning R? Statistics? Education knowledge? Data science?

---

class: middle

## The book is structured into project-based learning, which has its benefits.

## Besides project-based learning, how else do you find the time and motivation to learn new things or keep up with different trends?

---

class: middle

# Chapter 19: Conclusion: Where to Next?

- Learn in the Context of Education
  - How do you identify a project or problem that needs your attention?
- Learn to Collaborate with Others
  - Do you have an education-related data science question and need help with it?
  - Learn to collaborate with your future self.
- Learn Every Time You Code
- Learn to Take Strategic Breaks to Help Solve Problems
- Learn More Meaningfully by Knowing Your Why

---

class: middle

# The Future of Data Science in Education

**The last few chapters of the book focuses on _personal actions_ to engage with data science in education. However, we learned from chapter 4 (and personal experience) that we must consider the larger context and systems.**
### What are some things you'd like to see the field of data science (generally) and DS in education (specifically) move toward in the next 3-5 years?


---

class: middle

# Sharing with our communities

---

class: middle

# Sharing with our communities

## What has been one take-away from reading this book?

---

class: middle

# Sharing with our communities

## What's one thing you wish everyone would/should know about ... ?  
### - using R, 
### - performing statistics, 
### - doing data science, or 
### - working in education

---

class: middle

# Sharing with our communities

## What advice would you give to the next DSIEUR book club cohort?

---
class: center, middle

# Thank you

# H.A.G.S.